Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-16 src/data-science-project/data_science_project/docs/report/report.tex
Business questions

\section{Business Questions}
The study aimed to address several business questions related to inventory management and demand forecasting:
\begin{itemize}
    \item What are our best and worst customers?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest1.png}
        \caption{Business Question 1}
        \end{center}
    \end{figure}

    \item What is the relationship between sales growth rates (1 and 2) and adjusted demand?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest2.png}
        \caption{Business Question 2}
        \end{center}
    \end{figure}

    \item How are our sales going against the returns, and our adjusted demand?

    % \begin{figure}[H] 
    %     \begin{center}
    %     \centering
    %     \includegraphics[width=0.7\textwidth]{images/quest2.png}
    %     \caption{Business Question 3}
    %     \end{center}
    % \end{figure}

    \item What are our most used routes?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest4.png}
        \caption{Business Question 3}
        \end{center}
    \end{figure}

>>>>

\section{Business Questions}
The study aimed to address several business questions related to inventory management and demand forecasting:
\begin{itemize}
    \item What are our best customers per week?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/question1.jpg}
        \caption{Business Question 1}
        \end{center}
    \end{figure}

    \item What are the sales that WAL MART TEPEYAC had during the weeks?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/question2.jpg}
        \caption{Business Question 2}
        \end{center}
    \end{figure}

    \item How many sales and returns where done for each week?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.7\textwidth]{images/question3.jpg}
        \caption{Business Question 3}
        \end{center}
    \end{figure}

    \item What are the top 10 products with most sales?

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/question4.jpg}
        \caption{Business Question 3}
        \end{center}
    \end{figure}
